Hydras \& Co.

### 2023-07-15 doc/chapter-fol.tex
work on chapter-natural-deduction

We can make this proof script shorter, using existential variables.

>>>>

\begin{figure}[h]
  \centering
  \[
  \infer{C}{ 
    \infer{B \arrow C}
    {\infer{ A \arrow B \arrow C}
      { A \arrow B \arrow C}
      &
      \infer{A}{A}}
    & \infer{B}{
      \infer{A\arrow B}{A\arrow B} &
      \infer{A}{A}}
                     }
\]
  \caption{The proof tree of \texttt{PrfEx2}}
  \label{fig:PrfEx2}
\end{figure}

Figure~\ref{fig:PrfEx2} shows the tree-like structure of 
\texttt{PrfEx2}. The list of used hypotheses is the fringe of the tree. The unary nodes are applications of \texttt{AXM} and the binary nodes are associated with \texttt{MP}.

We can make our  proof script shorter, using existential variables.
